---
title: "ENA Rotation (Examples)"
author: "Zhiqiang Cai"
date: "`r format(Sys.Date(), '%B %d, %Y')`"
output:
  bookdown::pdf_document2:
    toc: true
    number_sections: true
    fig_caption: true
    latex_engine: xelatex
geometry: margin=1in
fontsize: 11pt
header-includes:
  - \usepackage{amsmath}
  - \usepackage{amssymb}
  - \usepackage{mathtools}
  - \usepackage{bm}
  - \usepackage{booktabs}
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(
  echo = TRUE,
  message = FALSE,
  warning = FALSE,
  fig.width = 6,
  fig.height = 4,
  dpi = 150
)
```

# Introduction

This document tests the newly added generalized rotation functionality in **rENA**. The rotation routines support several ways to determine each ENA dimension:

-   **SVD** — maximize total variance.

-   **BG / BG2 / BGC / BGC2** — maximize between-group variance (options for selecting two groups and for controlling covariates).

-   **RN / RN2 / RNC / RNC2** — regress on a numeric variable (options for selecting two groups and for controlling covariates).

There are 9 reasonable choices for each of the first and second dimensions, yielding 9×9=81 possible combinations. This report does **not** exhaustively test all 81 combinations. Instead, it executes a carefully chosen subset that exercises each major branch in the generalized rotation code. While not definitive, these tests cover representative cases and provide reasonable confidence that the implementation behaves as intended.

We would like to put two important notes here:

-   This document may not be friendly for careful reading, because of the heavy code chunks. Readers may have a quick scan and have hands on using the accompanying Rmd file, if interested, of course.

-   In the cases that an option yields a zero rotation vector, no ENA set is created. The process stops.


# Setup, Data and Unitility Functions

```{r}
library(rENA)
library(tidyverse)
```

Load and prepare the Rescue Shell (RS) data used throughout the tests.

```{r}
data(RS.data)

RS.data <- RS.data %>%
filter(CONFIDENCE.Change %in% c(0,1,2,3))

RS.data$CONFIDENCE.Change <- as.numeric(RS.data$CONFIDENCE.Change)

codes <- c(
'Data',
'Technical.Constraints',
'Performance.Parameters',
'Client.and.Consultant.Requests',
'Design.Reasoning',
'Collaboration'
)

accum <- ena.accumulate.data(
units = RS.data[, c("Condition", "GroupName", "UserName")],
conversation = RS.data[, c("Condition", "GroupName")],
metadata = RS.data[, c("CONFIDENCE.Change", "GroupName", "Condition")],
codes = RS.data[, codes],
model = "EndPoint",
window.size.back = 4
)

# convenience: create the default SVD set once

set_svd <- ena.make.set(enadata = accum)

A <- as.matrix(set_svd$model$points.for.projection)
V_svd <- as.matrix(set_svd$rotation$rotation.matrix)
A_rotated_svd <- as.matrix(set_svd$points)

Condition <- set_svd$meta.data$Condition
GroupName <- set_svd$meta.data$GroupName
CONFIDENCE.Change <- set_svd$meta.data$CONFIDENCE.Change

```

Utility Functions

```{r}
# Align column signs of V1 to V (in case that columns differ only by sign)

align_signs <- function(V_ref, V_target) {
  # Convert to matrices
  V_ref <- as.matrix(V_ref)
  V_target <- as.matrix(V_target)

  # Check dimensions
  if (!all(dim(V_ref) == dim(V_target))) {
    stop("align_signs(): V_ref and V_target must have identical dimensions.")
  }

  # Compute sign for each column
  # inner product per column
  s <- colSums(V_ref * V_target)

  # Avoid zero sign
  s[s == 0] <- 1

  # Align signs: multiply each column of V_target by s
  V_target_aligned <- sweep(V_target, 2, sign(s), `*`)

  return(V_target_aligned)
}


# Check all almost-zero

is_zero <- function(x, tol = 1e-12) all(abs(x) < tol)

# Between-group scatter matrix

between_scatter <- function(A, g) {
A <- as.matrix(A)
stopifnot(length(g) == nrow(A))
mu <- colMeans(A)
S_B <- matrix(0, ncol(A), ncol(A))
for (grp in unique(g)) {
A_k <- A[g == grp, , drop = FALSE]
n_k <- nrow(A_k)
mu_k <- colMeans(A_k)
d <- mu_k - mu
S_B <- S_B + n_k * tcrossprod(d)
}
S_B
}

# Mean difference vector for two-group case (normalized)

mean_diff_vec <- function(A, g, groups) {
stopifnot(length(groups) == 2)
m1 <- colMeans(A[g == groups[1], , drop = FALSE])
m2 <- colMeans(A[g == groups[2], , drop = FALSE])
v <- m1 - m2
v / sqrt(sum(v^2))
}

# Orthogonalize v to the list of vectors `vecs`, then normalize

orthogonalize <- function(v, vecs = list()) {
for (u in vecs) {
if (!is_zero(u)) {
u <- u / sqrt(sum(u^2))
v <- v - as.numeric(t(v) %*% u) * u
}
}
v / sqrt(sum(v^2))
}

# Deflate A by projector on v (v must be unit length or will be normalized)

deflate_matrix <- function(A, v) {
v <- v / sqrt(sum(v^2))
A - A %*% v %*% t(v)
}

# Verification helper: align signs, compare, print summary

verify_vector <- function(v_expected, v_model, label = NULL) {
v_expected <- align_signs(v_model, v_expected)
equal <- is_zero(v_expected - v_model)
cos_sim <- as.numeric(t(v_expected) %*% v_model)
if (!is.null(label)) cat("\nVerification: ", label)
cat("\n  Identical (within tol)? ", equal)
cat("\n  Cosine similarity: ", round(cos_sim, 6))
invisible(list(equal = equal, cosine = cos_sim))
}

```

# Testing strategy (what's tested)

We test:

-   **First-dimension**: SVD and each generalized rotation option (BG, BG2, BGC, BGC2, RN, RN2, RNC, RNC2). For each, we replicate the computation used by rENA (SVD / means / regression / Lasso main-effect ) and compare the resulting vector to `set$rotation$rotation.matrix[,1]`.

-   **Second-dimension**: using a representative first-dimension choice (`BGC2`) we test second-dimension options that exercise factor-based and numeric-based Y variables (BG, BGC, RN, RNC). For second-dimension tests we explicitly orthogonalize to the first dimension and to the group mean-difference direction where appropriate, matching rENA's deflation/orthogonalization order.


# First-dimension tests

All tests follow the pattern:

1.  build `set` with `ena.rotate.by.generalized` and appropriate `rotation.params`,

2.  extract `V <- set$rotation$rotation.matrix`,

3.  compute the "manual" direction `v1` (SVD, mean difference, Lasso/main-effect, regression, etc.),

4.  align signs and compare using `verify_vector()`.

## SVD (baseline)

```{r}
# Already constructed above as set_svd

V <- as.matrix(set_svd$rotation$rotation.matrix)

# Manual SVD on A

svd_manual <- svd(A)
V_manual <- svd_manual$v
V_manual <- align_signs(V, V_manual)

# verify rotation matrix equality

verify_vector(V_manual[,1], V[,1], "SVD: first column")

# verify rotated points

A_manual_rot <- A %*% V_manual
cat("\nA vs A_rotated identical? ", is_zero(A_manual_rot - A_rotated_svd))

```

## BG — between-group direction (GroupName)

```{r}
set_bg <- ena.make.set(
enadata = accum,
rotation.by = ena.rotate.by.generalized,
rotation.params = list(x_var = as.data.frame(GroupName))
)
V_bg <- as.matrix(set_bg$rotation$rotation.matrix)

S_B <- between_scatter(A, GroupName)
v1 <- svd(S_B)$v[,1]
verify_vector(v1, V_bg[,1], "BG (GroupName)")
```

## BG2 — between two selected groups

```{r}
#set.seed(2025)
selected_groups <- sample(unique(GroupName), 2)

set_bg2 <- ena.make.set(
enadata = accum,
rotation.by = ena.rotate.by.generalized,
rotation.params = list(x_var = as.data.frame(GroupName),
select_2_groups = selected_groups)
)
V_bg2 <- as.matrix(set_bg2$rotation$rotation.matrix)

v1 <- mean_diff_vec(A, GroupName, selected_groups)
verify_vector(v1, V_bg2[,1], paste0("BG2 (groups: ", paste(selected_groups, collapse=", "), ")"))

```

## BGC — between-group controlling for Condition (uses main-effect Lasso)

```{r}
X <- data.frame(GroupName = GroupName, Condition = Condition)
set_bgc <- ena.make.set(
enadata = accum,
rotation.by = ena.rotate.by.generalized,
rotation.params = list(x_var = X)
)
V_bgc <- as.matrix(set_bgc$rotation$rotation.matrix)

# rENA uses get_x1_main_effect (Lasso-ish). Recompute A1 then between scatter.

A1 <- rENA::get_x1_main_effect(A, X)
S_B <- between_scatter(A1, GroupName)
v1 <- svd(S_B)$v[,1]

res <- verify_vector(v1, V_bgc[,1], "BGC (GroupName controlling Condition)")

# check cosine as additional evidence when not identical

if (!res$equal) message("  cosine:", res$cosine)

```

In this test, our independently computed direction shows a small difference from the rENA result. This is normal. When covariates are present, the Lasso regression used to obtain the rotation direction may return slightly different solutions across runs, especially when multiple solutions fit the data equally well. These variations do not affect substantive interpretation, as the resulting directions remain extremely similar.

## BGC2 — between-group (2 groups) controlling for Condition

```{r}
#set.seed(2025)
selected_groups <- sample(unique(GroupName), 2)

X <- data.frame(GroupName = GroupName, Condition = Condition)
set_bgc2 <- ena.make.set(
enadata = accum,
rotation.by = ena.rotate.by.generalized,
rotation.params = list(x_var = X, select_2_groups = selected_groups)
)
V_bgc2 <- as.matrix(set_bgc2$rotation$rotation.matrix)

A_sub <- A[GroupName %in% selected_groups, , drop = FALSE]
X_sub <- X[GroupName %in% selected_groups, , drop = FALSE]
Group_sub <- GroupName[GroupName %in% selected_groups]

A1_sub <- rENA::get_x1_main_effect(A_sub, X_sub)
v1 <- mean_diff_vec(A1_sub, Group_sub, selected_groups)

verify_vector(v1, V_bgc2[,1], paste0("BGC2 (selected: ", paste(selected_groups, collapse=", "), ")"))

```

## RN — regress on numeric CONFIDENCE.Change

```{r}
X <- data.frame(CONFIDENCE.Change = CONFIDENCE.Change)
set_rn <- ena.make.set(
enadata = accum,
rotation.by = ena.rotate.by.generalized,
rotation.params = list(x_var = X)
)
V_rn <- as.matrix(set_rn$rotation$rotation.matrix)

# Linear regression of each column of A on CONFIDENCE.Change

fit <- lm(A ~ CONFIDENCE.Change)
beta <- fit$coefficients[2,]        # slope vector across A's columns
v1 <- beta / sqrt(sum(beta^2))

verify_vector(v1, V_rn[,1], "RN (regress on CONFIDENCE.Change)")

```

## RN2 — regress on CONFIDENCE.Change with two selected levels (e.g., 0 and 3)

```{r}
selected_levels <- c(0, 3)

X <- data.frame(CONFIDENCE.Change = CONFIDENCE.Change)
set_rn2 <- ena.make.set(
enadata = accum,
rotation.by = ena.rotate.by.generalized,
rotation.params = list(x_var = X, select_2_groups = selected_levels)
)
V_rn2 <- as.matrix(set_rn2$rotation$rotation.matrix)

A_sub <- A[CONFIDENCE.Change %in% selected_levels, , drop = FALSE]
CONF_sub <- CONFIDENCE.Change[CONFIDENCE.Change %in% selected_levels]

fit <- lm(A_sub ~ CONF_sub)
beta <- fit$coefficients[2,]
v1 <- beta / sqrt(sum(beta^2))

verify_vector(v1, V_rn2[,1], paste0("RN2 (conf levels: ", paste(selected_levels, collapse=", "), ")"))

```

## RNC — regress on CONFIDENCE.Change controlling for Condition (with interactions option)

```{r}
X <- data.frame(CONFIDENCE.Change = as.numeric(CONFIDENCE.Change), Condition = Condition)
set_rnc <- ena.make.set(
enadata = accum,
rotation.by = ena.rotate.by.generalized,
rotation.params = list(x_var = X)
)
V_rnc <- as.matrix(set_rnc$rotation$rotation.matrix)

# Recompute A1 using Lasso main effect + interactions, then regress on CONFIDENCE.Change

A1 <- rENA::get_x1_main_effect(A, X, include_interactions = TRUE)
fit <- lm(A1 ~ as.numeric(CONFIDENCE.Change))
beta <- fit$coefficients[2,]
v1 <- beta / sqrt(sum(beta^2))

verify_vector(v1, V_rnc[,1], "RNC (regress on CONFIDENCE.Change controlling Condition)")

```

## RNC2 — regress on CONFIDENCE.Change with two selected levels and controlling for Condition

```{r}
selected_levels <- c(0, 3)
X <- data.frame(CONFIDENCE.Change = CONFIDENCE.Change, Condition = Condition)
set_rnc2 <- ena.make.set(
enadata = accum,
rotation.by = ena.rotate.by.generalized,
rotation.params = list(x_var = X, select_2_groups = selected_levels)
)
V_rnc2 <- as.matrix(set_rnc2$rotation$rotation.matrix)

A_sub <- A[CONFIDENCE.Change %in% selected_levels, , drop = FALSE]
X_sub <- X[CONFIDENCE.Change %in% selected_levels, , drop = FALSE]
CONF_sub <- CONFIDENCE.Change[CONFIDENCE.Change %in% selected_levels]

A1_sub <- rENA::get_x1_main_effect(A_sub, X_sub, include_interactions = TRUE)
fit <- lm(A1_sub ~ CONF_sub)
beta <- fit$coefficients[2,]
v1 <- beta / sqrt(sum(beta^2))

verify_vector(v1, V_rnc2[,1], paste0("RNC2 (selected conf: ", paste(selected_levels, collapse=", "), ")"))

```
# Second-dimension tests (representative cases)

We assume the first dimension is produced by a BGC2 (GroupName + Condition, two selected groups), then test several representative second-dimension methods on top of that deflation. These cases exercise how rENA creates a second dimension after deflation and orthogonalization.

For reproducibility in these examples we set a seed before sampling two groups.

```{r}
set.seed(2025)
selected_groups <- sample(unique(GroupName), 2)
X <- data.frame(GroupName = GroupName, Condition = Condition)
```

## 1. Case: BGC2 (first) + BG (second, factor CONFIDENCE.Change)

```{r}
Y_factor <- data.frame(CONFIDENCE.Change = as.factor(CONFIDENCE.Change))
set_bg_second <- ena.make.set(
enadata = accum,
rotation.by = ena.rotate.by.generalized,
rotation.params = list(
x_var = X,
select_2_groups = selected_groups,
y_var = Y_factor
)
)
V2 <- as.matrix(set_bg_second$rotation$rotation.matrix)

# Recompute step-by-step:

A_sub <- A[GroupName %in% selected_groups, , drop = FALSE]
X_sub <- X[GroupName %in% selected_groups, , drop = FALSE]
Group_sub <- GroupName[GroupName %in% selected_groups]

# 1) first-dimension (means on A1)

A1 <- rENA::get_x1_main_effect(A_sub, X_sub)
S_B <- between_scatter(A1, Group_sub)
v1 <- svd(S_B)$v[,1]
v1 <- align_signs(V2[,1], v1)  # align sign to V2 first col

# 2) deflate original A by v1

A_def <- deflate_matrix(A, v1)

# 3) compute Y main effect on deflated matrix

A_def_1 <- rENA::get_x1_main_effect(A_def, Y_factor)
S_B_def <- between_scatter(A_def_1, as.factor(CONFIDENCE.Change))
v2 <- svd(S_B_def)$v[,1]

# 4) orthogonalize v2 to v1 and to group mean-diff

md <- mean_diff_vec(A_sub, Group_sub, selected_groups)
v2 <- orthogonalize(v2, list(v1, md))
v2 <- align_signs(V2[,2], v2)

verify_vector(v2, V2[,2], paste0("Second dim: BGC2 + BG (selected: ", paste(selected_groups, collapse=", "), ")"))

```

## Case: BGC2 + BGC (second, factor CONFIDENCE.Change + Condition)

```{r}
Y_factor_cond <- data.frame(CONFIDENCE.Change = as.factor(CONFIDENCE.Change), Condition = Condition)
set_bgc_second <- ena.make.set(
enadata = accum,
rotation.by = ena.rotate.by.generalized,
rotation.params = list(
x_var = X,
select_2_groups = selected_groups,
y_var = Y_factor_cond
)
)
V2b <- as.matrix(set_bgc_second$rotation$rotation.matrix)

# recompute v1 (same as previous)

A1 <- rENA::get_x1_main_effect(A[GroupName %in% selected_groups, , drop=FALSE],
X[GroupName %in% selected_groups, , drop=FALSE])
S_B <- between_scatter(A1, GroupName[GroupName %in% selected_groups])
v1 <- svd(S_B)$v[,1]
v1 <- align_signs(V2b[,1], v1)

# deflate and compute second dimension with interactions

A_def <- deflate_matrix(A, v1)
A_def_1 <- rENA::get_x1_main_effect(A_def, Y_factor_cond, include_interactions = TRUE)
S_B_def <- between_scatter(A_def_1, as.factor(CONFIDENCE.Change))
v2 <- svd(S_B_def)$v[,1]
md <- mean_diff_vec(A[GroupName %in% selected_groups, , drop=FALSE],
GroupName[GroupName %in% selected_groups],
selected_groups)
v2 <- orthogonalize(v2, list(v1, md))
v2 <- align_signs(V2b[,2], v2)

verify_vector(v2, V2b[,2], paste0("Second dim: BGC2 + BGC (selected: ", paste(selected_groups, collapse=", "), ")"))

# note: Lasso randomness may make v2 close but not exact

A21 <- rENA::get_x1_main_effect(A_def, Y_factor_cond, include_interactions = TRUE)
A22 <- rENA::get_x1_main_effect(A_def, Y_factor_cond, include_interactions = TRUE)
cat("\nmax(abs(A21 - A22)) (Lasso variation): ", max(abs(A21 - A22)))

```

## Case: BGC2 + RN (second, numeric)

```{r}
Y_num <- as.numeric(CONFIDENCE.Change)
set_rn_second <- ena.make.set(
enadata = accum,
rotation.by = ena.rotate.by.generalized,
rotation.params = list(
x_var = X,
select_2_groups = selected_groups,
y_var = data.frame(CONFIDENCE.Change = Y_num)
)
)
V2c <- as.matrix(set_rn_second$rotation$rotation.matrix)

# recompute first-dimension v1

A1 <- rENA::get_x1_main_effect(A[GroupName %in% selected_groups, , drop=FALSE],
X[GroupName %in% selected_groups, , drop=FALSE])
S_B <- between_scatter(A1, GroupName[GroupName %in% selected_groups])
v1 <- svd(S_B)$v[,1]
v1 <- align_signs(V2c[,1], v1)

A_def <- deflate_matrix(A, v1)
A_def_1 <- rENA::get_x1_main_effect(A_def, data.frame(CONFIDENCE.Change = Y_num), include_interactions = TRUE)

# If rENA does numeric second-dimension by regression:

fit <- lm(A_def_1 ~ Y_num)
v2 <- fit$coefficients[2,]
v2 <- v2 / sqrt(sum(v2^2))

md <- mean_diff_vec(A[GroupName %in% selected_groups, , drop=FALSE],
GroupName[GroupName %in% selected_groups],
selected_groups)
v2 <- orthogonalize(v2, list(v1, md))
v2 <- align_signs(V2c[,2], v2)

verify_vector(v2, V2c[,2], paste0("Second dim: BGC2 + RN (selected: ", paste(selected_groups, collapse=", "), ")"))

```

## Case: BGC2 + RNC (second, numeric + Condition)

```{r}
Y_num_cond <- data.frame(CONFIDENCE.Change = as.numeric(CONFIDENCE.Change), Condition = Condition)
set_rnc_second <- ena.make.set(
enadata = accum,
rotation.by = ena.rotate.by.generalized,
rotation.params = list(
x_var = X,
select_2_groups = selected_groups,
y_var = Y_num_cond
)
)
V2d <- as.matrix(set_rnc_second$rotation$rotation.matrix)

# recompute first dim

A1 <- rENA::get_x1_main_effect(A[GroupName %in% selected_groups, , drop=FALSE],
X[GroupName %in% selected_groups, , drop=FALSE])
S_B <- between_scatter(A1, GroupName[GroupName %in% selected_groups])
v1 <- svd(S_B)$v[,1]
v1 <- align_signs(V2d[,1], v1)

A_def <- deflate_matrix(A, v1)
A_def_1 <- rENA::get_x1_main_effect(A_def, Y_num_cond, include_interactions = TRUE)
fit <- lm(A_def_1 ~ as.numeric(CONFIDENCE.Change))
v2 <- fit$coefficients[2,]
v2 <- v2 / sqrt(sum(v2^2))

md <- mean_diff_vec(A[GroupName %in% selected_groups, , drop=FALSE],
GroupName[GroupName %in% selected_groups],
selected_groups)
v2 <- orthogonalize(v2, list(v1, md))
v2 <- align_signs(V2d[,2], v2)

verify_vector(v2, V2d[,2], paste0("Second dim: BGC2 + RNC (selected: ", paste(selected_groups, collapse=", "), ")"))

```
# Test of rENA::get_x1_main_effect function
The above tests are under the assumption that get_x1_main_effect works correctly. What if that is not true? The following chunk tests this core function exaustively.
```{r}
# Load necessary library
library(glmnet)

# --- Test Helper: Generate Data with Known Components ---
generate_test_data <- function(n = 100, p = 5, interaction_strength = 5) {
  X <- as.data.frame(matrix(rnorm(n * p), n, p))
  colnames(X) <- paste0("x", 1:p)
  
  # Ground Truth: x1 has a main effect of 2
  # There is a heavy interaction between x1 and x2
  true_main_effect <- 2 * X$x1
  interaction_effect <- interaction_strength * (X$x1 * X$x2)
  
  V <- as.matrix(true_main_effect + interaction_effect + rnorm(n, sd = 0.1))
  colnames(V) <- "Target"
  
  return(list(X = X, V = V, true_main = true_main_effect))
}

# --- 1. The "Logic Consistency" Test ---
# If we include interactions in the model, the contribution of x1 
# should still be close to the TRUE main effect (2 * x1).
test_logic <- function() {
  data <- generate_test_data()
  res <- rENA::get_x1_main_effect(data$V, data$X, include_interactions = TRUE)
  
  # Correlation should be very high with the true main effect, NOT the total V
  cor_val <- cor(res[,1], data$true_main)
  message("Logic Test: Cor(Estimated, True Main) = ", round(cor_val, 4))
  stopifnot(cor_val > 0.95)
}

# --- 2. The "Factor Variable" Stress Test ---
# Tests if the regex catches multiple dummy columns (x1LevelB, x1LevelC)
test_factors <- function() {
  n <- 100
  X <- data.frame(
    x1 = factor(sample(c("A", "B", "C"), n, replace = TRUE)),
    x2 = rnorm(n)
  )
  # Assign specific values to levels B and C
  V <- matrix(0, n, 1)
  V[X$x1 == "B", 1] <- 10
  V[X$x1 == "C", 1] <- -10
  V <- V + rnorm(n, sd = 0.1)
  
  res <- rENA::get_x1_main_effect(V, X, include_interactions = FALSE)
  
  # If it works, the mean contribution for group B should be ~10
  mean_b <- mean(res[X$x1 == "B", 1])
  message("Factor Test: Mean Contribution Level B = ", round(mean_b, 2))
  stopifnot(abs(mean_b - 10) < 0.5)
}

# --- 3. The "High Dimensional" Stress Test (P > N) ---
# Tests if Lasso correctly handles forcing x1 in when there are too many variables
test_high_dim <- function() {
  n <- 30
  p <- 100 # More variables than observations
  X <- as.data.frame(matrix(rnorm(n * p), n, p))
  colnames(X) <- paste0("x", 1:p)
  V <- matrix(rnorm(n), n, 1)
  
  # This should not crash and should return a non-zero matrix
  res <- rENA::get_x1_main_effect(V, X)
  stopifnot(nrow(res) == n, any(res != 0))
  message("High-Dim Test: Passed (No crash, non-zero output)")
}

# --- 4. The "Multi-Response" Test ---
# Tests if the function handles V as a matrix correctly
test_multi_response <- function() {
  data <- generate_test_data()
  V_multi <- cbind(data$V, data$V * 2) # Second column is just double the first
  colnames(V_multi) <- c("V1", "V2")
  
  res <- rENA::get_x1_main_effect(V_multi, data$X)
  
  stopifnot(ncol(res) == 2)
  # The second column should be roughly twice the first
  ratio <- mean(res[,2] / res[,1], na.rm = TRUE)
  message("Multi-Response Test: Ratio V2/V1 = ", round(ratio, 2))
  stopifnot(abs(ratio - 2) < 0.1)
}

# --- Run All Tests ---
test_logic()
test_factors()
test_high_dim()
test_multi_response()
message("ALL TESTS PASSED EXHAUSTIVELY!")
```

# Summary & Cautionary note

This report tests a **representative subset** of rotation combinations rather than the complete 9×9=81 grid. The selected tests intentionally exercise:

-   SVD-based rotation (baseline).

-   Between-group rotations with and without covariates and with selective two-group modes (BG, BG2, BGC, BGC2).

-   Regression-based rotations with and without covariates and two-group selection (RN, RN2, RNC, RNC2).

-   Lasso-main-effect and fallback regression paths used by `rENA::get_x1_main_effect`.

Because the tests cover each major branch, they offer **reasonable confidence** in the correctness of the generalized rotation implementation. However, they are **not exhaustive**. Additional tests may be needed if any issue comes out. 


